### 2014-11-11 model.tex
edits

When \emph{foo} is invoked on a object $x$ with arguments \emph{arg}$_1$ at
replica 1, it simply \emph{reduces} over the current set of effects at that
replica on that object ($w^x_1$ and $w^x_2$), produces a result $v1$ that is
sent back to the client, and emits a \emph{single} new effect $w^x_4$ that is
appended to the state of $x$ at replica 1. Thus, every operation is evaluated
over a \emph{snapshot} of the state of the object on which it is invoked. In
this case, the effects $w^x_1$ and $w^x_2$ are \emph{visible} to $w^x_4$,
written logically as $\small \vis{w^x_1}{w^x_4} \wedge \vis{w^x_2}{w^x_4}$, where
$\small \visZ$ is the visibility relation between effects. Visibility is an
irreflexive and asymmetric relation, and only relates effects produced by
operations on the same object. Executing a read-only operation is similar
except that no new effects are produced.

The effect added to a particular replica is asynchronously sent to other
replicas, and eventually merged into all other replicas. Two effects $w^x_4$
and $w^x_5$ that arise from the same session are said to be in \emph{session
order} (written logically as $\small \so{w^x_4}{w^x_5}$). Session order is an
irreflexive, transitive relation. The effects $w^x_4$ and $w^x_5$ arising from
operations applied to the same object $x$ are said to be under the \emph{same
object} relation, written $\small \sameobj{w^x_4}{w^x_5}$. Finally, we can
associate every effect with the operation that generated the effect with the
help of a relation $\small \operZ$. In the current example, $\small
\oper{w^x_4}{foo}$ and $\small \oper{w^x_5}{bar}$ hold. For simplicity, we
assume all operation names across all object are distinct.

>>>>

When \emph{foo} is invoked on a object $x$ with arguments \emph{arg}$_1$ at
replica 1, it simply \emph{reduces} over the current set of effects at that
replica on that object ($w^x_1$ and $w^x_2$), produces a result $v1$ that is
sent back to the client, and emits a \emph{single} new effect $w^x_4$ that is
appended to the state of $x$ at replica 1. Thus, every operation is evaluated
over a \emph{snapshot} of the state of the object on which it is invoked. In
this case, the effects $w^x_1$ and $w^x_2$ are \emph{visible} to $w^x_4$,
written logically as $\small \vis{w^x_1}{w^x_4} \wedge \vis{w^x_2}{w^x_4}$,
where $\small \visZ$ is the visibility relation between effects. Visibility is
an irreflexive and asymmetric relation, and only relates effects produced by
operations on the same object. Executing a read-only operation is similar
except that no new effects are produced. The effect added to a particular
replica is asynchronously sent to other replicas, and eventually merged into
all other replicas. Observe that this model does not assume a particular
resolution strategy for concurrent conflicting updates, and instead preserves
\emph{every} update. Conflicts are resolved when an operation reduces over the
set of effects on an object at a particular replica.

Two effects $w^x_4$ and $w^x_5$ that arise from the same session are said to be
in \emph{session order} (written logically as $\small \so{w^x_4}{w^x_5}$).
Session order is an irreflexive, transitive relation. The effects $w^x_4$ and
$w^x_5$ arising from operations applied to the same object $x$ are said to be
under the \emph{same object} relation, written $\small \sameobj{w^x_4}{w^x_5}$.
Finally, we can associate every effect with the operation that generated the
effect with the help of a relation $\small \operZ$. In the current example,
$\small \oper{w^x_4}{foo}$ and $\small \oper{w^x_5}{bar}$ hold. For simplicity,
we assume all operation names across all object are distinct.
